% !TEX encoding = UTF-8 Unicode
%!TEX root = ../Main/thesis.tex
% !TEX spellcheck = en-US
%%=========================================
\documentclass[../Main/thesis.tex]{subfiles}
\begin{document}
\null\vfill
\addcontentsline{toc}{chapter}{Abstract}
\chapter*{Abstract}
Machine of all sorts without doubt, have been and still are the driving force of the world economy, since the industrial revolution.
Operating in harsh conditions, machines are prone to failure, consequently incurring financial losses, and in worse cases, the degradation of the environment and the loss of human life. 
\justify
 One of the main component of nearly all machines are bearings. Due to their  geometrical characteristics, the latter facilitate rotation movements while being continuously subjected to large loads . Consequently, bearing failures represent more than 40$\%$ of machine breakdown. To mitigate
 bearing degradation, a set of sensors mounted on strategics area surrounding the bearings, collect vibration signals periodically. Each vibration signal is converted to its frequency spectrum through the Fourier transform. The latter is a corner stone in bearing fault detection. This is due to the fact that bearings faults occur at specific frequencies, called characteristic defect frequencies, which are derived from the bearing geometrical features. A defect in a bearing will emit a periodic high frequency pulse as the bearing rotates. The frequency at which the pulse is emitted is the characteristic defect frequency.
 As a result, the core of bearing monitoring, is the early detection of onset of failure, expressed in the characteristic fault frequencies, that can be found in the frequency spectrum, derived by the Fourier transform.
 \justify
 Bearings are in general mounted on machines comprising several components, each emitting its own vibration signal.
 This render the detection of defect frequencies in a bearing frequency spectrum challenging, due to interfering  signals, inducing noise. Therefore, the frequency spectrum obtained directly from a bearing vibration signal contains little diagnostic information. To circumvent the latter issue, a series of signal filtering and mathematical transformations are applied to a raw bearing vibration signal, in order to isolate and expose the relevant signal, that contains the defects frequencies. This process can be achieved though the so called high frequency resonance technique (HFRT) method. The bulk of the HFRT is to remove or dump irrelevant signals before applying the Fourier transform in order to generate a clean bearing frequency spectrum, that reveals the defect frequency.
 \justify
 Although efficient in bearing fault detection, the HFRT relies solely on the Fourier transform to obtain the frequency spectrum. Since the Fourier transform operates in the frequency domain, it ignores local temporal events such as pulses emitted by bearing faults. As a consequence, the frequency spectrum obtained is often noisy. To circumvent this problem, This thesis introduce the Hilbert Huang transform (HHT) for bearing fault detection. As opposed to the Fourier transform, the HHT operates in the time domain. It is not bound by predefined basis functions such as trigonometric extensions in Fourier transform. This property allows the Hilbert Huang transform to adaptively decomposed a signal in the time domain, in terms of nearly mono component signals. Here adaptively means there is no basis functions for the decomposition. This gives the Hilbert Huang transform a leverage over the Fourier transform, as it is able to reveal salient properties of data in the time domain, such as pulses emitted by bearing defects.
 \justify
 In this thesis, by applying the Hilbert Huang transform to bearing fault detection, a completely noise less frequency spectrum is extracted from the bearing vibration signal, and the bearings failure frequencies are clearly identifiable. With the present method, pulses emitted by bearing failure can be visualized, allowing a better analysis in bearing fault detection.
%Two methods for bearings fault detection are presented. Namely: Hilbert Huang transform and wavelet transform coupled with machine learning. Hilbert Huang transform is a data decomposition procedure, that uses local properties of a signal, to iteratively extract its sub-components. It deals with non-linearity and non-stationary with ease by design. It is coupled with a robust seasonal trend decomposition method, to extract high frequency short duration pulses, emitted by a crack located in the outer ring of a bearing. Wavelet transform on the other hand, uses a priori basis functions called wavelets, to decompose and reconstruct signals. It extracts both temporal and frequency information, and is able to \say{zoom in} and \say{zoom out} of data. The former and the latter properties are due to a scaling factor build in wavelet by design.
%We coupled wavelet transform with support vector machine, which is a linear classification algorithm, to monitor and detect bearing defect for a system of four bearings.

\vfill\vfill
\clearpage
\blankpage

\end{document}
